\section{Problems} \label{sec:problems}
While we tested our different approaches, we unfortunately ran into some problems. We will list them here.
\begin{itemize}
	\item The initial installation and setup of the platform proved to be very cumbersome. It took a long time and required us to set up a new, fresh linux installation.
	\item There are unpredictable crashes. While the crashes were unpredictable in when they happened, they happened frequently enough that we could not run our algorithm for more than about 40 movements. 
	\item Even hard coded movements are not deterministic in the outcome they provide. This proved to be a problem especially for the MCMC inspired algorithm, as it found ways to exploit glitches instead of properly learning. Also, some movements that were otherwise very good received a very low fitness because the movements glitched somehow.
	\item The grasp plugin for the hand did not work very well. The hand sometimes disappeared with the cylinder after deleting the cylinder, leading the simulation to eventually crash. Also the hand started vibrating severely if the grasp was too strong, and the cylinder just slipped when it was too weak.
	\item The delays between the status updates of the simulation increased with simulation time and the simulation got slower with each movement. Because the simulation quite reliably crashed when resetting it a few times, we had to rely on the platform calling back to the algorithm with updates such as "The simulation is resetting". As the status updates got slower and slower, the discrepancy between the status as observed by the algorithm and the actual status inside the simulation grew and led to some funny inconsistencies.
\end{itemize}